\documentclass[11pt]{article}
 

\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{algorithmicx,color,xspace,xcolor,fullpage,url}
\usepackage{framed}
\usepackage{comment}
\usepackage{booktabs}


\input{def}

\title{\bf iDASH Secure Genome Analysis Competition \\
Using {\sf ObliVM}}
\author{Xiao Shaun Wang, Chang Liu, Kartik Nayak, Yan Huang and Elaine Shi}
\date{University of Maryland, College Park\\
{\tt \{wangxiao,liuchang,kartik,elaine\}@cs.umd.edu, yh33@indiana.edu}
\\[10pt]
({\bf Online short note in supplement to our ObliVM paper~\cite{oblivm}}).}
\begin{document}
\maketitle
\section{Overview}
For problems in iDASH Secure Genome Analysis Competition~\cite{idash}, we implemented them using the secure computation framework {\sf ObliVM}\footnote{\url{http://www.oblivm.com}}~\cite{oblivm}.
For each question, we provide multiple solutions, with manually built circuits and automatically built circuits:
\begin{enumerate}
\item Task 1a: we provide two solutions, one built manually, one built using compiler. Both of them achieve exact result with no error.
\item Task 1b: we provide three solutions, two built manually, one built using compiler. The second manually built circuit can achieve a trade-off between efficiency and accuracy.
\item Tasks 2a and 2b: we provide four solutions, one built manually using oblivious merge, one built with compiler using oblivious merge, one built manually using bloom filter, and one built using compiler. The one with bloom filter can be tuned for a trade-off between efficiency and accuracy.
\end{enumerate}

Detailed instructions on how to run the program can be found in {\tt README.md}.
All the implementations will be open sourced at \url{https://github.com/wangxiao1254/idash_competition} after the deadline of the competition.



\paragraph{Manual vs. compiler-generated code.}
For optimal speed, please run our manually optimized code. 
Our compiler-generated code  
results in $1\%$ to $2\%$ 
larger circuit sizes than the manually optimized code.
The difference in actual running time is slightly larger
because the compiler generates longer 
instruction sequences (in Java)
to execute the circuits
than our manually optimized code. 
Further compiler backend optimizations can be performed 
to compress our target instruction sequence -- this will 
be part of our future work.

Nevertheless, we include our compiler-generated implementations
to demonstrate the ease-of-use of {\sf ObliVM}'s source language.




\input{task1}
\input{task2}
%\section{Conclusion}

\newpage
\appendix

\section*{\Large Supplemental Information}
\section{{\sf ObliVM} Overview}

{\sf ObliVM} is a programming framework for secure computation, offering the 
following features:
\begin{itemize}
\item
{\bf Ease-of-use.} Non-specialist programmers can easily 
write programs in our source language {\sf ObliVM-lang}, a 
familiar imperative-style language.
\item
{\bf Efficiency.} {\sf ObliVM} compiles these programs into 
concise circuit representations suitable for secure computation. 
Much as MapReduce is a programming paradigm for 
parallel computation, {\sf ObliVM} offers user- and compiler- friendly
programming abstractions for secure computation.
\item
{\bf Formal security.}
{\sf ObliVM} offers a security type system to ensure 
that programs supplied by nonspecialist developers
will be executed securely without leaking information.
At a high level, the security type system guarantees
that a program's execution traces 
is oblivious to secret inputs.
\end{itemize}

\paragraph{Capabilities of {\sf ObliVM}.} 
{\sf ObliVM} supports richer and much more sophisticated applications
than the challenges given in this competition.
We have developed a variety of demo applications in machine learning,
streaming algorithms, graph algorithms, 
common data structures, and common utilities.
Using {\sf ObliVM}, we have demonstrated queries on {\sf GB} 
databases where we can compute the answers in a reasonable amount of time. 


%\paragraph{Whitepaper and more resources.}
\vspace{10pt}
For more information about {\sf ObliVM} and additional resources,
please refer to our whitepaper  

\begin{center}
\url{http://oblivm.com/papers/oblivm.pdf}
\end{center}

and our website 

\begin{center}
\url{http://oblivm.com}
\end{center}


\section{Thank You and Suggestions to the Organizers}
We think this competition is such a fantastic idea. 
It definitely helps to bridge communities, and helps 
state-of-the-art secure computation technology  
find its way in high-impact application domains.
We are grateful to the organizers for organizing this competition,
and for detailed discussions and feedback 
throughout.

We really hope that more competitions like this will be held in the future.
If a competition like this is to be repeated, we 
urge that the organizers increase the difficulty 
of the challenges --- e.g., consider much more sophisticated tasks
and bigger data sizes. 
We feel that the simple and small-scale nature of the problems  
in this competition is insufficient to fully demonstrate the true power
of state-of-the-art secure computation frameworks such as {\sf ObliVM}.

\begin{comment}
\section{List of Programs and their Usage}
Here we list all the programs submitted. Please refer to the {\tt README.md} file 
for set up and the recommended programs for each task.

%Here we show the list of programs for each tasks we submitted:\\
\noindent\textbf{Task 1a:}\\

\noindent Exact solution (add {\tt -a} for automatically generated circuits):\\
Generator: {\tt ./run.py gen task1a -c path\_case1 -t path\_control1}\\
Evaluator: {\tt ./run.py eva task1a -c path\_case2 -t path\_control2}\\

\noindent\textbf{Task 1b:}\\
\begin{enumerate}
\item Run manually created circuit:\\
Generator: {\tt ./run.py gen task1b -c path\_case1 -t path\_control1}\\
Evaluator: {\tt ./run.py eva task1b -c path\_case2 -t path\_control2}

\item Run automatically created circuit:\\
Generator: {\tt ./run.py gen task1b -c path\_case1 -t path\_control1 -a}\\
Evaluator: {\tt ./run.py eva task1b -c path\_case2 -t path\_control2 -a}

\item Run manually created circuit with higher precision:\\
Generator: {\tt ./run.py gen task1b -c path\_case1 -t path\_control1 -h}\\
Evaluator: {\tt ./run.py eva task1b -c path\_case2 -t path\_control2 -h}

\end{enumerate}

\noindent\textbf{Task 2a:}\\
\begin{enumerate}
\item Solution using oblivious merge (add {\tt -a} for automatically generated circuits, {\tt -p NUMBER} where {\tt NUMBER} is the security parameter for hash collision):\\
Generator: {\tt ./run.py gen task2astd -f path\_file}\\
Evaluator: {\tt ./run.py eva task2astd -f path\_file}

\item Solution using bloom filter (add {\tt -a} for automatically generated circuits, {\tt -p NUMBER} for a trade off between precision and speed. {\tt NUMBER} is M/N in bloom filter.):\\
Generator: {\tt ./run.py gen task2abf -f path\_file}\\
Evaluator: {\tt ./run.py eva task2abf -f path\_file}

\end{enumerate}


\noindent\textbf{Task 2b:}\\
\begin{enumerate}
\item Solution using oblivious merge (add {\tt -a} for automatically generated circuits, {\tt -p NUMBER} where {\tt NUMBER} is the security parameter for hash collision.):\\
Generator: {\tt ./run.py gen task2bstd -f path\_file}\\
Evaluator: {\tt ./run.py eva task2bstd -f path\_file}

\item Solution using bloom filter (add {\tt -a} for automatically generated circuits, {\tt -p NUMBER} for a trade off between precision and speed. {\tt NUMBER} is M/N in bloom filter.):\\
Generator: {\tt ./run.py gen task2bbf -f path\_file}\\
Evaluator: {\tt ./run.py eva task2bbf -f path\_file}
\end{enumerate}



task2a:
---------------------
 -  

 -  

task2b:
---------------------
 -  




 -  
\end{comment}
\bibliographystyle{plain}
\bibliography{refs,bibdiffpriv,bibliography,crypto,ref}


\end{document} 





